Environment modeling in \tool

### 2022-05-02 paper.tex
minor fix

Approaches above only investigate which part of the environment should be modeled but neglect the question of how to model the environment. \tool is a symbolic execution compiler that translates the programs from Source Language S to Target language T. Intuitively, we can choose to model the environment in the Source Language (as part of the user program) or in the Target Language (as runtime library). Like KLEE, we choose to model the environment in the system call level with a symbolic file system. Using the flexibility of our framework, we can choose between directly poring KLEE' file system or developing an internal file system in the backend.\par

@@

In section \ref{evaluation}, we present benchmarks of Coreutils programs in our engine with two file system implementations and KLEE.\par

@@

\section{Different levels of Environment Modeling}\label{twofsimpl}

@@

 KLEE's file system is a hybrid approach. It contains both symbolic files and concrete files. It maintains symbolic metadata like offset and open flags for symbolic and concrete files. For symbolic files, it will allocate a char array buffer upon creation to store its symbolic content and a symbolic stat struct to store its symbolic status. For concrete files, it will record its actual file descriptor upon opening for future references.\par

@@

Implementing the file system at the source language level has the advantages of portability and flexibility. It can be ported to a completely different framework with little effort without the need to mangle with the underlying internal engine details. We can also switch more flexibly between different designs. For example, we can enable symbolic filenames simply by making the filename symbolic, and no modification in the file system is required. The underlying symbolic engine will deal with the state forking as it analyzes our file system code with the user code after linking. However, to achieve the same goal in the target language level implementation, we will need to understand the internal control representation (direct style or CPS-style) and modify the open system call in the runtime library to handle the possible forking of states accordingly.\par

@@

The dynamic scheduling in some analysis pass causes another compilation time overhead. Because LMS uses a Sea of Nodes IR, each IR node is not statically assigned to blocks. Instead, the nodes are connected through data and effect dependencies and can move freely as long as it does not violate the dependencies. The base class of analyzer in LMS is a traverser, and it will dynamically schedule the IR every time to calculate the IR of each block. For large-scale graphs, dynamic scheduling takes up most of the analysis and optimization time. As a case study, we can look at the AssignElimination optimization pass where we try to eliminate unused local stack variables. This pass consists of a traverser to filter out the unused stack variable and a transformer to rebuild the optimized graph. This optimization needs to schedule the graph twice because both the traverser and transformer will schedule the graph. As a result, the whole optimization takes about 70s for echo program while 60s of it is spent on the scheduling. However, we can perform the optimization without scheduling the whole graph in the analysis traverser. After rewriting the analysis procedure, we can reduce the entire optimization time to 40s. \par

@@

\tool generates a C++ file for each function in the analyzed program, which favors multi-core compilation. For example, the fully linked echo program will be compiled into 155 C++ files. As a result, it is beneficial to use multi-core processors and exploit parallel compilation. Although most of the files can be compiled very quickly, the compilation of the main file will get stuck when optimization is enabled. Our engine will pre-process the global data into an extensive list and put it in front of the actual heap in a large vector as the initial symbolic heap. Each vector element is a pointer to the actual value (concrete or symbolic) created by a corresponding wrapper function. After profile and debug, we observe that the initialization list of the sizeable pre-heap vector will be first allocated on the stack. Each vector element has to be assigned by calling the corresponding initialization function. The body of the main function is enormous, and the optimization will get stuck. Furthermore, a specific optimization pass SROA (replacement of aggregates) will try to split the sizeable stack-allocated object into pieces to fit them inside registers. This pass will try to analyze the large stack-allocated initialization list and stall the entire compilation. This problem is unavoidable in our current implementation without a complete rewrite of the code generation strategy. We choose only to use O0 to compile the main file and O3 to compile other generated programs to bypass this problem. This will not affect the overall runtime performance as the main function is a start-up procedure for the entire symbolic execution and is only a one-time effort. We will see some concrete evidence from benchmarks compared to KLEE in Section \ref{evaluation}.

@@

After diagnosing the cause of compilation time overhead in the Scala part and the C++ part and fixing them accordingly, we can compile the entire program into executable files in less than two minutes. This amount of time is acceptable compared to more than 10 minutes in the un-optimized before. We can now test more Coreutils programs and achieve fast-iteration over the test-fix-verify procedure.

@@

This section shows the evaluation benchmarks of running Coreutils programs on \tool with two file systems and KLEE. \tool has two file system implementations, one written at the source language level (directly reusing KLEE's POSIX filesystem) and one written at the target language level as runtime library. We also run the same program on KLEE to compare the performance with \tool. Because we directly reuse KLEE's file system as the source level implementation, comparisons between \tool with KLEE's POSIX file system and KLEE is fair and can measure the efficiency of these two symbolic execution engines. We will use \tool/POSIX to represent our framework with KLEE's filesystem implementation, \tool/FS to represent our framework with the internal file system implementation, and KLEE/POSIX to represent KLEE with its file system. We choose echo from Coreutils programs for testing, and we perform all the experiments on the Intel(R) Xeon(R) Platinum 8168 CPU @ 2.70GHz 192 core CPU on server bigdata2.cs.purdue.edu. We use g++ with -O3 to compile the generated C++ code as mentioned in section \ref{coreutilstests}. The running time is shown in Table \ref{tab:coreutils_benchmarks_echo} and Figure \ref{fig:speedup}.\par

>>>>

Approaches above only investigate which part of the environment should be modeled but neglect the question of how to model the environment. \tool is a symbolic execution compiler that translates the programs from Source Language S to Target language T. Intuitively, we can choose to model the environment in the Source Language (as part of the user program) or in the Target Language (as runtime library). Like KLEE, we choose to model the environment in the system call level with a symbolic file system. Thanks to the flexibility of our framework, we can choose between directly poring KLEE' file system and developing an internal file system in the backend.\par

@@

In section \ref{evaluation}, we present benchmarks of running Coreutils programs in our engine with two file system implementations and in KLEE.\par

@@

\section{Different implementations of Environment Modeling}\label{twofsimpl}

@@

 KLEE's file system is a hybrid approach. It contains both symbolic files and concrete files. It manages metadata like offset and open flags for symbolic and concrete files. For symbolic files, it will allocate a char array buffer upon creation to store its symbolic content and a symbolic stat struct to store its symbolic status. For concrete files, it will record its actual file descriptor upon opening for future references.\par

@@

Implementing the file system at the source language level has the advantages of portability and flexibility. It can be ported to a completely different framework without the need to mangle with the underlying internal engine details. We can also switch more flexibly between different designs. For example, we can enable symbolic filenames simply by making the filename symbolic, and no modification in the file system is required. The underlying symbolic engine will deal with the state forking as it analyzes our file system code with the user code after linking. However, to achieve the same goal in the target language implementation, we will need to understand the internal control representation (direct style or CPS-style) and modify the open system call in the runtime library to handle the possible forking of states accordingly.\par

@@

The dynamic scheduling in some analysis pass causes another compilation time overhead. Because LMS uses a Sea of Nodes IR, each IR node is not statically assigned to blocks. Instead, the nodes are connected through data and effect dependencies and can move freely as long as it does not violate the dependencies. The base class of analyzer in LMS is a traverser, and it will dynamically schedule the IR every time to calculate the IR of each block. For large-scale graphs, dynamic scheduling takes up most of the analysis and optimization time. As a case study, we can look at the AssignElimination optimization pass where we try to eliminate unused local stack variables. This pass consists of a traverser to filter out the unused stack variable and a transformer to rebuild the optimized graph. This optimization needs to schedule the graph twice because both the traverser and transformer will schedule the graph. As a result, the whole optimization takes about 80s for echo program while more than 60s of it is spent on the scheduling. However, we can perform the optimization without scheduling the whole graph in the analysis traverser. After rewriting the analysis procedure, we can reduce the entire optimization time to about 50s. \par

@@

\tool generates a C++ file for each function in the analyzed program, which favors multi-core compilation. For example, the fully linked echo program will be compiled into 155 C++ files. As a result, it is beneficial to use multi-core processors and exploit parallel compilation. Although most of the files can be compiled very quickly, the compilation of the main file will get stuck when optimization is enabled. Our engine will pre-process the global data into an extensive list and put it in front of the actual heap in a large vector as the initial symbolic heap. Each vector element is a pointer to the actual value (concrete or symbolic) created by a corresponding wrapper function. After profiling and debugging, we observe that the initialization list of the sizeable pre-heap vector will be first allocated on the stack. Each vector element has to be assigned by calling the corresponding initialization function. As a result, the body of the main function is enormous, and the optimization will get stuck. Furthermore, a specific optimization pass SROA (scalar replacement of aggregates) will try to split the sizeable stack-allocated object into pieces to fit them inside registers. This pass will try to analyze the large stack-allocated initialization list and stall the entire compilation. This problem is unavoidable in our current implementation without a complete rewrite of the code generation strategy. We choose only to use O0 to compile the main file and O3 to compile other generated programs to bypass this problem. This will not affect the overall runtime performance as the main function is a start-up procedure for the entire symbolic execution and is only a one-time effort. We will compare the performance of \tool with KLEE in Section \ref{evaluation}.

@@

After diagnosing the cause of compilation time overhead in the Scala part and the C++ part and fixing them accordingly, we can compile the entire program into executable files in less than two minutes. This amount of time is acceptable compared to more than 10 minutes before. We can now test more Coreutils programs and achieve fast-iteration over the test-fix-verify procedure.

@@

This section shows the evaluation benchmarks of running Coreutils programs on \tool with two file system implementations and KLEE. \tool has two file system implementations, one written at the source language level (directly reusing KLEE's POSIX filesystem) and one written at the target language level as runtime library. We also run the same program on KLEE to compare the performance with \tool. Because we directly reuse KLEE's file system, comparisons between \tool with KLEE's POSIX file system and KLEE is fair and can measure the efficiency of these two symbolic execution engines. We will use \tool/POSIX to represent our framework with KLEE's filesystem implementation, \tool/FS to represent our framework with the internal file system implementation, and KLEE/POSIX to represent KLEE with its file system. We choose echo from Coreutils programs for testing, and we perform all the experiments on the Intel(R) Xeon(R) Platinum 8168 CPU @ 2.70GHz 192 core CPU on server bigdata2.cs.purdue.edu. We use g++ with -O3 to compile the generated C++ code as mentioned in section \ref{coreutilstests}. The running time is shown in Table \ref{tab:coreutils_benchmarks_echo} and Figure \ref{fig:speedup}.\par
